### 2020-08-20 8_case_study.tex
Rewrite TensorFlow case study.

Initial experiments with TensorFlow revealed that the Task
Bench implementation was not able to use all cores on a node (making it impossible to measure METG since efficiency was below
50\%). The TensorFlow developers diagnosed this as an issue in
constant folding. The entire Task Bench task graph was being detected
as constant, and the constant-folding pass runs on one core. As a
workaround, the developers suggested marking the task graph inputs as
non-constant so that TensorFlow's standard task scheduler could be
used.

>>>>

The Task Bench implementation for TensorFlow uses aggressive loop
unrolling to minimize overhead, and this initially resulted in the
entire graph being marked constant. TensorFlow performs optimizations
on task graphs prior to execution, including a constant folding
pass. These optimizations are performed on a single core. In the case
of Task Bench, this resulted in sequential execution of the entire
graph, resulting in experiments timing out. As a workaround,
additional inputs can be fed to nodes in the graph to make them
non-constant, forcing them to be executed by TensorFlow's normal
scheduler. Though this was exacerbated by Task Bench's approach to
unrolling loops, it affects any task graph with constants that are
expensive to compute where the users may wish to perform
constant-folding in parallel.

\zap{
Initial experiments with TensorFlow revealed that the Task
Bench implementation was not able to use all cores on a node (making it impossible to measure METG since efficiency was below
50\%). The TensorFlow developers diagnosed this as an issue in
constant folding. The entire Task Bench task graph was being detected
as constant, and the constant-folding pass runs on one core. As a
workaround, the developers suggested marking the task graph inputs as
non-constant so that TensorFlow's standard task scheduler could be
used.
}
